Classifying Activities Using Body-Worn Accelerometers for Real-Time Application

### 2016-05-23 notes/paper/paper.tex
Arranged text lines in paper to one line.

Body worn sensors have been used in the market for many years now. Most of which are used specifically for activity monitoring or fitness. In this paper, we present a method for real-time activity classification, from accelerometers worn by the user, by using the matched-filter method. We also discuss the methods used to improve computational efficiency, and the unsupervised learning method for training the device to recognize motion patterns provided by the user.

@@

e manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction. We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane. By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our x and y axis accordingly. Because most common activities are mostly confined to two dimensions, this will improve our signal identification.

>>>>

Body worn sensors have been used in the market for many years now. Many of which are used for activity monitoring or fitness. In this paper, we present a method for real-time activity classification using a matched-filter algorithm from data obtained with three-axis accelerometers worn by the user.  We achieve invariance to sensor orientation and improve computational efficiency with dimensionality reduction. An instance-based learning algorithm is used to train the device to learn the individual's motion patterns.

@@

We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction. We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.  By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our x and y axis accordingly. Because most common activities are mostly confined to two dimensions, this will improve our signal identification.
